How to Avoid OOTA Without Really Trying

### 2024-09-12 paper/ootavacuous.tex
ootavacuous: Further rework abstract
Reported-by: Alan Stern <stern@rowland.harvard.edu>
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

	We focus on shared-memory programs and C++ implementations based
	on traditional compilers and hardware, including CPUs and GPGPUs,
	thus easing analysis of semantic dependencies and OOTA behaviors
	via existing hardware models.
	We show that these models' constraints prevent OOTA cycles from
	occurring in undefined-behavior-free C++ programs running on
	compiler-based implementations that use single-thread analysis,
	provided the cycles involve only volatile atomics.
	We also extend this work to nonvolatile atomics by defining
	``quasi-volatile'' behavior that C++ implementations must adhere
	to in order to evaluate arithmetic expressions involving atomic
	accesses in accordance with the standard.

>>>>

	We focus on shared-memory programs and C++ implementations based
	on traditional compilers and hardware, including CPUs and GPGPUs,
	thus enabling analysis of semantic dependencies and OOTA behaviors
	by means of existing hardware models.
	We show that these models' constraints prevent OOTA cycles from
	occurring in undefined-behavior-free C++ programs running on
	such implementations, provided the cycles involve only volatile
	atomics.
	For implementations doing only single-threaded analysis, we
	accommodate nonvolatile atomics by defining ``quasi-volatile''
	behavior that must be adhered to in order to evaluate arithmetic
	expressions involving atomic accesses in accordance with the
	standard.
